Reanalysis Step 4: Main Effects Outcome Analysis

### 2025-08-28 reanalysis-4-outcome_analysis.qmd
better x-axis
fix

library(mice)
library(survey)
library(broom)
library(marginaleffects)
library(emmeans)
library(tidyr)

@@

library(ggplot2)

@@

@@

# Add annotation showing stabilization
if (n_imputations >= 10) {
  # Calculate when estimate stabilized (when running avg changes < 1%)
  running_changes <- abs(diff(imputation_estimates$running_avg_OR) / 
                         imputation_estimates$running_avg_OR[-1])
  stabilized_at <- which(running_changes < 0.01)[1]

  if (!is.na(stabilized_at) && stabilized_at < n_imputations - 5) {
    convergence_plot <- convergence_plot +
      geom_vline(xintercept = stabilized_at, linetype = "dotted", alpha = 0.5) +
      annotate("text", x = stabilized_at, y = max(imputation_estimates$OR) * 0.98,
               label = paste0("Stabilized (~", stabilized_at, ")"),
               hjust = -0.1, size = 3.5)
  }
}

>>>>

library(mice)
library(survey)
library(broom)
library(marginaleffects)
library(emmeans)
library(tidyr)
library(ggplot2)

@@

@@

  # Make x-axis show only integers
  scale_x_continuous(breaks = function(x) {
    seq(from = ceiling(x[1]), to = floor(x[2]), by = max(1, floor((x[2] - x[1]) / 10)))
  }) +

@@
